Multi-level modeling with Openflexo/\FML

### 2021-10-13 10-conclusions.tex

\noteSM{Say that the flexibility of our approach coupled with a methodology allows us to achieve multi/level capabilities without specific tooling in order to solve problems which require it.}

>>>>

\textcolor{red}{The features of \FML enable a great modelling flexibility which, coupled with an appropriate methodology, allow us to achieve
the multi/level capabilities without dedicated tooling in order to solve problems which require it. We use virtual models to "implement" levels on demand.}
%\noteSM{Say that the flexibility of our approach coupled with a methodology allows us to achieve multi/level capabilities without specific tooling in order to solve problems which require it.}
